Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 main.tex
started to move proofs to appendix; removing dependency on minted
add page numbers
restructuring
comments
todo list
rename todo list
rewritten the introduction
remove section 5
removing tdo files
title
eliminate TODOs in introduction; improve formatting of title
proofs of Lemmas 1 and 2
implementation paragraph in section 4; stats table in section 2; removed section 5
new abstract

@@

\title{Data Flow Analysis\\in the Presence of Correlated Calls}

@@

\pagenumbering{gobble}

@@

\begin{abstract}
We present a technique to improve the precision of data-flow analyses on object-oriented programs in the presence of 	\textit{correlated calls}. Two method calls are correlated if they are polymorphic and are invoked on the same object. Correlated calls are problematic because they can make  existing data-flow analyses consider certain infeasible data-flow paths as valid. This leads to loss in precision of the analysis solution.

We show how infeasible paths can be eliminated for \textit{Inter-procedural Finite Distributive Subset} (IFDS) problems, a large class of data-flow analysis problems. We show how the precision of IFDS problems can be improved in the presence of correlated calls, by using the \textit{Inter-procedural Distributive Environment} (IDE) algorithm to eliminate infeasible paths.  Using IDE, we eliminate the infeasible paths and obtain a more precise result for the original IFDS problem.

Our analysis is implemented in Scala, using the WALA framework for static program analysis on Java bytecode.

%\keywords{We would like to encourage you to list your keywords within
%the abstract section}
\end{abstract}

\input{content/intro}
\input{content/background}
\input{content/impl}
\input{content/datastr}
\input{content/eval}
\input{content/concl}

\bibliographystyle{plain}
\bibliography{bib/ref}
\end{document}

>>>>

\pagenumbering{gobble}
\listoftodos[Overview of Comments]

@@

\title{Precise Data Flow Analysis\\in the Presence of Correlated Method Calls}
\titlerunning{Data Flow Analysis in the Presence of Correlated Calls}

@@

\pagenumbering{arabic}

@@

\input{content/abstract}
\input{content/intro}
\input{content/example}
\input{content/background}
\input{content/impl}
%\input{content/datastr}
%\input{content/eval}
\input{content/related}
\input{content/concl}

\bibliographystyle{plain}
\bibliography{bib/ref}

\input{content/appendix}
\end{document}
